\begin{multicols}{2}
\subsection{{Timsort Algorithm Explained --- \href{https://virgool.io/@liewpl/timsort-algorithm-explained-u41h0wv0jnax}{link}}}
\begin{zitemize}
\item Full coverage and explanation for {\ttfamily timsort} algorithm.
\end{zitemize}
%====================

\subsection{{Let's Write a Tokenozer and Parser --- \href{https://virgool.io/@liewpl/tokenizer-parser-in-python-ubzlsvukmdxz}{link}}}
\begin{zitemize}
\item A comprehensice walk through of studing the theory of automata, writing a RegEx, drawing a DFA and implementing a tokenizer and a parser out of them.
\end{zitemize}
%====================

\subsection{{What's New in Python 3.12 --- \href{https://virgool.io/@liewpl/python-3-12-whats-new-vpq99njtytc6}{link}}}
\begin{zitemize}
\item Point to point, PEP to PEP and issue to issue of \textit{What's new} in Python 3.12 stable release.
\end{zitemize}
%====================

\subsection{{Deep Dive Into Object and Types in the C Layer of CPython}}
\begin{zitemize}
\item How objects and types are implemented in CPython?
\item written in \href{https://virgool.io/@liewpl/cpython-objs-types-c-layer-deep-dive-m5fjelhzrzny}{Persian}
\& \href{https://virgool.io/@liewpl/cpython-objs-types-c-layer-deep-dive-m5fjelhzrzny}{English}
\end{zitemize}
%====================

\subsection{{How list.append Works In CPython's C Layer?}}
\begin{zitemize}
\item How does CPython do an {\ttfamily list.append} exactly?
\item written in \href{https://virgool.io/@liewpl/how-append-works-gp4apwtpr0bt}{Persian}
\& \href{https://medium.com/@mahdihaghverdi/how-list-append-is-implemented-in-c-layer-of-cpython-interpreter-bf88632819c0}{English}
\end{zitemize}
%====================

\subsection{{Python is TOO Fast --- \href{https://virgool.io/@liewpl/python-is-very-fast-gmmdjs3zyhob}{link}}}
\begin{zitemize}
\item Is Python fast or slow? Let's have a discussion.
\end{zitemize}
%====================

\subsection{{Python asyncio And TaskGroups --- \href{https://virgool.io/@liewpl/asyncio-and-taskgroups-t598c8poken9}{link}}}
\begin{zitemize}
\item Python {\ttfamily asyncio} module has a new type (from 3.11) called {\ttfamily TaskGroup}. Let's see why it was important to have it in stdlib.
\end{zitemize}
%====================

\subsection{{Python Standard Library vs. PyPI --- \href{https://virgool.io/@liewpl/asyncio-and-taskgroups-t598c8poken9}{link}}}
\begin{zitemize}
\item How Python stdlib differs from PyPI?
\end{zitemize}
%====================

\subsection{{Python, A Language For Companies Seeking High Performance --- \href{https://vrgl.ir/29p56}{link}}}
\begin{zitemize}
\item Should the High-tech companies and startups use Python for their product or not?
\end{zitemize}
%====================

\subsection{{CPython Will Be 5x Times Faster --- \href{https://virgool.io/@liewpl/cpython-five-times-faster-p5jve4zzywog}{link}}}
\begin{zitemize}
\item How faster CPython team will improve the performance of Python?
\end{zitemize}
%====================

\subsection{{More in here: \href{https://virgool.io/@liewpl/}{https://virgool.io/@liewpl/}}}
%====================

\end{multicols}